Corrections

### 2020-09-30 changes_highlighted.tex
Save changes mid way

\section{Preliminaries and Notation}\label{section:prelim}

The theoretical foundations for inverse problems over function spaces
can be found in \cite{Stuart10}. This section is mostly devoted to
setting notation. \reftwo{\sout{At this point, it is useful to record a known result
regarding the posterior covariance operator of our inverse problem,
namely}
\begin{align}\label{eq:postcov precursor}
  \stkout{\postcov = (\prcov^{-1} + \fwd^* \obs^* \Sigma^{-1} \obs \fwd )^{-1}.}
\end{align}
}

@@

\section{The Constrained Optimization Problem of D-Optimal Design}\label{section:D and grad}
From \eqref{eq:objective} we wish to characterize solution(s) of the
following optimization problem for $\tar$. %%: (\ban^*)^m \to \R$:
\begin{align}\label{eq:optimization}
  \obs^{\star} := \argmax_{\obs} \tar( \obs ) 
  = \argmax_{\obs} \frac12 \log \det 
  (I + \prcov^{1/2} \fwd^*\obs^* \Sigma^{-1} \obs \fwd \prcov^{1/2}),
\end{align}
where $\obs$ is constrained to some allowed set of measurements
(e.g.\ pointwise evaluations on $[0,\pi]$).
%%, for the example in section \ref{subsec:example}).
We seek a formulation of the optimal design using Lagrange
multipliers. In section \ref{section:objective} we find the gradient
of $\tar$. In section \ref{subsec:unit length} we relax the
constraints on $\obs$ so that the optimization problem in
\eqref{eq:optimization} \reftwo{is analytically tractable} and find
gradients for the new constraints.

@@

\section{Analysis of Optimal Designs --- Vanishing Model Error}\label{section:vanishing}
When $\modcov = 0$, then $\Sigma= \sigma^2I$. The necessary
first-order condition for optimality \eqref{eq:conditions} becomes
\begin{equation}\label{eq:eigenproblem}
  \sigma^{-2}\fwd \postcov \fwd^* \obs^* = \obs^* \Xi, 
\end{equation}
with $\Xi$ diagonal. This is an eigenvalue problem for the
self-adjoint operator $\sigma^{-2}\fwd \postcov \fwd^*$ where the rows
of $\obs$, namely $\meas_j,j=1,\dots, m$, are the
eigenvectors. \refthree{Below, we use \eqref{eq:postcov} in the second
  equality.} If $\fwd$ is invertible, \refthree{\sout{then we may
    write} the third equality is trivial. Otherwise, we use some
  calculations delegated to lemma \ref{lemma:twice woodbury} in the
  appendix}:
\begin{align}\label{eq:mod conditions}
  \begin{split}
  \obs^* \Xi &= \sigma^{-2}\fwd \postcov \fwd^* \obs^*  \\
  %
  %
  %
  &= \sigma^{-2} \fwd( \prcov^{-1} + \sigma^{-2}  \fwd^* \obs^* \obs \fwd )^{-1} \fwd^* \obs^* \\
  %
  %
  %
  &= \sigma^{-2} \left ( (\fwd\prcov\fwd^*)^{-1} + \sigma^{-2}  \obs^* \obs \right )^{-1} \obs^*
  \end{split}
\end{align}  
\refthree{\sout{which} This} presents the optimal design problem as a
problem on $\ban$ and not on $\hil$ --- the term $(\fwd \prcov
\fwd^*)^{-1}$ is the prior precision in $\ban$ and \reftwo{\sout{the
    big parentheses enclose} $(\fwd\prcov\fwd^*)^{-1} + \sigma^{-2}
  \obs^* \obs$ is} the posterior precision in
$\ban$. \refthree{\sout{This expression makes sense even if $\fwd$ is
    not invertible --- consider instead $\fwd$ restricted to $\ker
    \fwd^{\perp}$. This does not change the optimal design problem at
    all, since we will never take measurements that have a component
    in $\ker \fwd$ (this can be understood from Corollary
    \ref{cor:zero mod err}).}}

\subsection{Characterizing D-Optimal Designs}\label{subsub:characterization}
In light of \eqref{eq:mod conditions}, let us denote eigenvalues of
$\fwd \prcov \fwd^*$ by $\lambda_1 \geq \lambda_2 \geq \dots$ and its
eigenvectors $\{\ev_i\}_{i=1}^{\infty}$. The following lemma (proved
in the appendix \ref{lemma:sim diag}) will be useful:

@@

\refthree{
\begin{align}%\label{eq:old pre manipulations}
  \cancel{
  \begin{split}
    I + \sigma^{-2} \prcov^{1/2} \fwd ^* \obs^*
    \obs \fwd \prcov^{1/2}\right ) &= \prcov^{1/2} ( \prcov^{-1} +
    \sigma^{-2} \fwd^*\obs^* \obs \fwd ) \prcov^{1/2} \\
    %
    %
    %
    &=\prcov^{1/2} \fwd^* ( \fwd^{-*}
    \prcov^{-1}\fwd^{-1} + \sigma^{-2} \obs^* \obs ) \fwd \prcov^{1/2}
    (\fwd\prcov\fwd^*)^{-1}\\
    %
    %
    %
    &= \prcov^{1/2} \fwd^* \left ( (\fwd \prcov \fwd^* )^{-1}
    +\sigma^{-2} \obs^* \obs \right ) \fwd \prcov^{1/2}.
  \end{split}
  }
\end{align}
}

\refthree{
\begin{align}\label{eq:pre manipulations}
  \begin{split}
    \det \left (I + \sigma^{-2} \prcov^{1/2} \fwd ^* \obs^*
    \obs \fwd \prcov^{1/2}\right ) &=
    %
    \det \left (  \fwd \prcov^{1/2}(I + \sigma^{-2} \prcov^{1/2} \fwd ^* \obs^*
    \obs \fwd \prcov^{1/2}) \prcov^{1/2} \fwd^* (\fwd \prcov \fwd^*)^{-1} \right ) \\
    %
    %
    %
    &= \det \left ( (\fwd \prcov \fwd^* + \sigma^{-2}\fwd \prcov
    \fwd^* \obs^*\obs \fwd \prcov \fwd^*) (\fwd \prcov \fwd^*)^{-1}
    \right )\\
    %
    %
    %
    &= \det \left ( ((\fwd \prcov \fwd^*)^{-1} + \sigma^{-2}
    \obs^*\obs ) (\fwd \prcov \fwd^*) \right )\\
  \end{split}
\end{align}
}

@@

The argument above has the important consequence that the eigenvalues
in \eqref{eq:eigenproblem} are all equal! This makes perfect
sense. First, we know the Lagrange multipliers tell us how much we
gain by relaxing the constraints and there is no reason for any
measurement to give us more than any other (otherwise we would put
more weight on the better measurement, as can be understood from the
discussion in the following paragraph).%%  We are also used to symmetric
%% optimization problems having symmetric solutions \cite{Waterhouse83},
%% so symmetric and identical Lagrange multipliers definitely make sense
%% in this context.

@@

\reftwo{Results of section \ref{subsub:characterization} specifically,
  the discussion at the end of said section, along with figure
  \ref{figure:clusterization} and eqaution \eqref{eq:true target} show
  how clusterization arises when an optimal design is saught.

  }
\section{Analysis of Optimal Designs --- Non-Vanishing Model Error}
Denote $\obs = (\meas_1,\dots,\meas_m)^t$ and $\obsm :=
(\meas_1,\dots,\meas_{m-1})^t$. The following corollary is proved in
appendix \ref{cor:same meas proof}.
\begin{restatable*}{corollary}{samemeas}\label{cor:same meas}.
  If $\meas_m = \meas_j$ for some $1 \leq j \leq m-1$, then
  \begin{equation*}
    \tar(\obs) - \tar(\obsm) =
    \log \left ( 1 + \frac{\sigma^2
      \langle \fwd \postcovm \fwd^* \obsm^* \Sigmam^{-1} e_j,
      \obsm^* \Sigmam^{-1}e_j \rangle
    }{
      2 - \sigma^2 e_j^t\Sigmam^{-1}e_j 
    }       
    \right ).
  \end{equation*}
\end{restatable*}

In contrast to the previous case of vanishing model error, we will see
that if $\modcov \neq 0$ clustering will not occur. From Corollary
\ref{cor:same meas} we can observe that as $\sigma^2 \to 0$, the
increase in the design criterion gained by taking a measurement
identical to a previous one approaches zero. We may conclude that for
small measurement error levels, the clusterization effect will be
mitigated by the presence of a non-zero model error. Since the design
criterion is not defined for $\sigma^2 = 0$ and identical
measurements, we cannot make a statement regarding $\sigma^2 = 0$,
except in the limiting sense described above.

@@

\section{Specific Lemmas}
\refthree{
\begin{lemma}\label{lemma:twice woodbury}
  Assume $\fwd \prcov \fwd^*$ is invertible. Then
\begin{align*}
  \begin{split*}
    \fwd( \prcov^{-1} + \sigma^{-2}  \fwd^* \obs^* \obs \fwd )^{-1} \fwd^* 
    %
    %
    = \left ( (\fwd\prcov\fwd^*)^{-1} + \sigma^{-2}  \obs^* \obs \right )^{-1},
  \end{split*}
\end{align*}  
\end{lemma}
\begin{proof}
  The proof is boring and amounts to using Woodbury's matrix identity
  twice and a regularization trick. The standard proof for this
  identity works in infinite dimensions, as long as all terms are well
  defined. Unfortunately, $\obs^*\obs$ is not invertible, so we force
  it to be. Throughout, we let $X := \fwd\prcov \fwd^*$ and $Y_{\eps}
  := \obs^*\obs + \eps I$, for some small $\eps > 0$. Note that now
  $Y_{\eps}$ is invertible. Recall Woodbury's matrix identity:
  $$
  (A + UCV)^{-1} = A^{-1} + A^{-1}U(C^{-1} + VA^{-1}U)^{-1}VA^{-1}.
  $$

>>>>

\section{Preliminaries and Notation}\label{section:prelim}
\reftwo{
\subsection{Overview}
The theoretical foundations for inverse problems over function spaces
can be found in \cite{Stuart10}. In this section we define notations that will be
  used throughout the paper.
%% A reader mostly familiar with the
%% literature may initially want to skip this section and only consult
%% the list below, which summarizes the notation used. We denote:
%% \begin{itemize}
%%   \item Parameter space $\hil$.
%%   \item Data space $\ban$.
%%   \item Forward dynamics operator $\fwd: \hil \to \ban$.
%%   \item Observation operator $\obs: \ban \to \mathbb{R}^m$.
%%   \item Prior measure $\pr = \mathcal{N}(0, \prcov)$.
%%   \item Data $\data \in \mathbb{R}^m$.
%%   \item Observation and model errors, captured in $\Sigma(\obs)$.
%% \end{itemize}
%% The design objective was derived in \cite{AlexanderianGloorGhattas14}
%% and recorded in \eqref{eq:objective} below.
\sout{At this point, it is useful to record a known result regarding
  the posterior covariance operator of our inverse problem, namely}
\begin{align}\label{eq:postcov precursor}
  \stkout{\postcov = (\prcov^{-1} + \fwd^* \obs^* \Sigma^{-1} \obs \fwd )^{-1}.}
\end{align}
}

@@

\section{The Constrained Optimization Problem of D-Optimal Design}\label{section:D and grad}

\subsection{\reftwo{Overview}}
From \eqref{eq:objective} we wish to characterize solution(s) of the
following optimization problem for $\tar$. %%: (\ban^*)^m \to \R$:
\begin{align}\label{eq:optimization}
  \obs^{\star} := \argmax_{\obs} \tar( \obs ) 
  = \argmax_{\obs} \frac12 \log \det 
  (I + \prcov^{1/2} \fwd^*\obs^* \Sigma^{-1} \obs \fwd \prcov^{1/2}),
\end{align}
where $\obs$ is constrained to some allowed set of measurements
(e.g.\ pointwise evaluations on $[0,\pi]$).
%%, for the example in section \ref{subsec:example}).
We seek a formulation of the optimal design using Lagrange
multipliers. In section \ref{section:objective} we find the gradient
of $\tar$ and record it in \eqref{eq:tar grad}. In section
\ref{subsec:unit length} we relax the constraints on $\obs$ so that
the optimization problem in \eqref{eq:optimization} \reftwo{is
  analytically tractable}.  We find gradients for the new constraints
\reftwo{and record them in \eqref{eq:grad constraints}. Finally, in
  section \ref{subsec:necessary} we use these to formulate the optimal
  design problem as a Lagrange multipliers problem in equation
  \eqref{eq:conditions}.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION Analysis of Optimal Designs --- Vanishing Model Error
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis of Optimal Designs --- Vanishing Model Error}\label{section:vanishing}
\subsection{\reftwo{Overview}}
\reftwo{In this section we analyze optimal designs when no model error
  is present. We show how sensor clusterization arises in section
  \ref{subsec:clusterization}. We prepare the ground by first deriving
  an eigenvalue problem in $\obs$ for an optimal design in section
  \ref{subsec:eigenproblem}. This eigenvalue problem is recorded in
  \eqref{eq:mod conditions}. Next, we characterize optimal designs as
  ones that make all eigenvalues in equal in the above mentioned
  eigenproblem. This is crucial for clusterization to occur. The
  derivation is presented in section \ref{subsec:characterization}. }

\subsection{\reftwo{The Eigenvalue Problem}}\label{subsec:eigenproblem}
When $\modcov = 0$, then $\Sigma= \sigma^2I$. The necessary
first-order condition for optimality \eqref{eq:conditions} becomes
\begin{equation}\label{eq:eigenproblem}
  \sigma^{-2}\fwd \postcov \fwd^* \obs^* = \obs^* \Xi, 
\end{equation}
with $\Xi$ diagonal. This is an eigenvalue problem for the
self-adjoint operator $\sigma^{-2}\fwd \postcov \fwd^*$ where the rows
of $\obs$, namely $\meas_j,j=1,\dots, m$, are the
eigenvectors. \refthree{Below, we use \eqref{eq:postcov} in the second
  equality.} If $\fwd$ is invertible, \refthree{\sout{then we may
    write} the third equality is trivial. Otherwise, we use some
  calculations delegated to lemma \ref{lemma:twice woodbury} in the
  appendix}:
\begin{align}\label{eq:mod conditions}
  \begin{split}
  \obs^* \Xi &= \sigma^{-2}\fwd \postcov \fwd^* \obs^*  \\
  %
  %
  %
  &= \sigma^{-2} \fwd( \prcov^{-1} + \sigma^{-2}  \fwd^* \obs^* \obs \fwd )^{-1} \fwd^* \obs^* \\
  %
  %
  %
  &= \sigma^{-2} \left ( (\fwd\prcov\fwd^*)^{-1} + \sigma^{-2}  \obs^* \obs \right )^{-1} \obs^*
  \end{split}
\end{align}  
\refthree{\sout{which} This} presents the optimal design problem as a
problem on $\ban$ and not on $\hil$ --- the term $(\fwd \prcov
\fwd^*)^{-1}$ is the prior precision in $\ban$ and \reftwo{\sout{the
    big parentheses enclose} $(\fwd\prcov\fwd^*)^{-1} + \sigma^{-2}
  \obs^* \obs$ is} the posterior precision in
$\ban$. \refthree{\sout{This expression makes sense even if $\fwd$ is
    not invertible --- consider instead $\fwd$ restricted to $\ker
    \fwd^{\perp}$. This does not change the optimal design problem at
    all, since we will never take measurements that have a component
    in $\ker \fwd$ (this can be understood from Corollary
    \ref{cor:zero mod err}).}}

\subsection{Characterizing D-Optimal Designs}\label{subsec:characterization}
In light of \eqref{eq:mod conditions}, let us denote eigenvalues of
$\fwd \prcov \fwd^*$ by $\lambda_1 \geq \lambda_2 \geq \dots$ and its
eigenvectors $\{\ev_i\}_{i=1}^{\infty}$. The following lemma (proved
in the appendix \ref{lemma:sim diag}) will be useful:

@@

\refthree{
  \begin{align}%\label{eq:old pre manipulations}
    \cancel{
      \begin{split}
        I + \sigma^{-2} \prcov^{1/2} \fwd ^* \obs^*
        \obs \fwd \prcov^{1/2} &= \prcov^{1/2} ( \prcov^{-1} +
        \sigma^{-2} \fwd^*\obs^* \obs \fwd ) \prcov^{1/2} \\
        %
        %
        %
        &=\prcov^{1/2} \fwd^* ( \fwd^{-*}
        \prcov^{-1}\fwd^{-1} + \sigma^{-2} \obs^* \obs ) \fwd \prcov^{1/2}
        (\fwd\prcov\fwd^*)^{-1} \\
        %
        %
        %
        &= \prcov^{1/2} \fwd^* \left ( (\fwd \prcov \fwd^* )^{-1}
        +\sigma^{-2} \obs^* \obs \right ) \fwd \prcov^{1/2}.
      \end{split}
    }
\end{align}
}

\refthree{
\begin{align}\label{eq:pre manipulations}
  \begin{split}
    \det \left (I + \sigma^{-2} \prcov^{1/2} \fwd ^* \obs^*
    \obs \fwd \prcov^{1/2}\right ) &=
    %
    \det \left (I + \sigma^{-2} \obs^*
    \obs \fwd \prcov\fwd^* \right ) \text{(Sylvester's determinant theorem)}\\
    %
    %
    %
    &= \det \left \{ \left ( (\fwd \prcov \fwd^*)^{-1} +
    \sigma^{-2}\obs^*\obs \right ) (\fwd \prcov \fwd^*)\right \}\\
  \end{split}
\end{align}
}

@@

The argument above has the important consequence that the eigenvalues
in \eqref{eq:eigenproblem} are all equal This makes perfect
sense. First, we know the Lagrange multipliers tell us how much we
gain by relaxing the constraints and there is no reason for any
measurement to give us more than any other (otherwise we would put
more weight on the better measurement, as can be understood from the
discussion in the following paragraph).%%  We are also used to symmetric
%% optimization problems having symmetric solutions \cite{Waterhouse83},
%% so symmetric and identical Lagrange multipliers definitely make sense
%% in this context.

@@

\reftwo{Results of section \ref{subsec:characterization} specifically,
  the discussion at the end of said section, along with figure
  \ref{figure:clusterization} and equation \eqref{eq:true target} show
  how clusterization arises when an optimal design is saught.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION Analysis of Optimal Designs --- Non-Vanishing Model Error
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis of Optimal Designs --- Non-Vanishing Model Error}
\subsection{\reftwo{Overview}}
In this section we show how clusterization is avoided when model
error does not vanish.

\subsection{\reftwo{Derivation}}
We rely on corollary \ref{cor:same meas} below, which is proved in the
appendix. Denote $\obs = (\meas_1,\dots,\meas_m)^t$ and $\obsm :=
(\meas_1,\dots,\meas_{m-1})^t$.
\begin{restatable*}{corollary}{samemeas}\label{cor:same meas}.
  If $\meas_m = \meas_j$ for some $1 \leq j \leq m-1$, then
  \begin{equation*}
    \tar(\obs) - \tar(\obsm) =
    \log \left ( 1 + \frac{\sigma^2
      \langle \fwd \postcovm \fwd^* \obsm^* \Sigmam^{-1} e_j,
      \obsm^* \Sigmam^{-1}e_j \rangle
    }{
      2 - \sigma^2 e_j^t\Sigmam^{-1}e_j 
    }       
    \right ).
  \end{equation*}
\end{restatable*}
 In
contrast to the previous case of vanishing model error, we will see
that if $\modcov \neq 0$ clustering will not occur. From Corollary
\ref{cor:same meas} we can observe that
\refthree{
$$
\lim_{\sigma^2 \to 0} \tar(\obs) -\tar(\obsm) = 0
$$ \sout{as $\sigma^2 \to 0$, the increase in the design criterion
  gained by taking a measurement identical to a previous one
  approaches zero}. Hence no increase in the design criterion is
achieved. This is clearly sub-optimal and $\obsm$ cannot be an optimal
design}. We may conclude that for small measurement error levels, the
clusterization effect will be mitigated by the presence of a non-zero
model error. Since the design criterion is not defined for $\sigma^2 =
0$ and identical measurements, we cannot make a statement regarding
$\sigma^2 = 0$, except in the limiting sense described above.

@@

\section{Specific Lemmas}
\refthree{
\begin{lemma}\label{lemma:twice woodbury}
  Assume $\fwd \prcov \fwd^*$ is invertible. Then
\begin{align*}
  \begin{split}
    \fwd( \prcov^{-1} + \sigma^{-2}  \fwd^* \obs^* \obs \fwd )^{-1} \fwd^* 
    %
    %
    = \left ( (\fwd\prcov\fwd^*)^{-1} + \sigma^{-2}  \obs^* \obs \right )^{-1},
  \end{split}
\end{align*}  
\end{lemma}
\begin{proof}
  The proof is boring and amounts to using Woodbury's matrix identity
  twice and a regularization trick. The standard proof for this
  identity works in infinite dimensions, as long as all terms are well
  defined. Unfortunately, $\obs^*\obs$ is not invertible, so we force
  it to be. Throughout, we let $X := \fwd\prcov \fwd^*$ and $Y_{\eps}
  := \obs^*\obs + \eps I$, for some small $\eps > 0$. Note that now
  $Y_{\eps}$ is invertible. Recall Woodbury's matrix identity:
  $$
  (A + UCV)^{-1} = A^{-1} + A^{-1}U(C^{-1} + VA^{-1}U)^{-1}VA^{-1}.
  $$

### 2020-09-30 reply.tex
Save changes mid way

@@

\begin{enumerate}
\item It should be stated in the Abstract whether the work in this
  paper pertains to only linear inverse problems, or if it is
  applicable in general to non-linear inverse problems as well.
  \ydnote{Title and abstract now reflect the fact that the paper only
    pertains to linear inverse problems.}

@@

\item In some equations (as seen below in the line comments) operators
are not clearly defined or described before they are given in a
proposition or theorem. Please clearly define all operators both with
mathematical definitions and descriptions (when applicable) before
using them. \ydnote{Corrected, thanks!}

\item Overall, I find the article difficult to follow. I think this can
be improved by properly defining all operators and including section
overviews that give a description of the purpose of each section, and
a brief summary of how this is being accomplished.

@@

\begin{itemize}
\item Page 1, Line 39: "In a frequentist settings" should be changed
  to "in a frequentist setting" or "in frequentist
  settings". \ydnote{changed in text}

@@

\item Page 3, Line 37: "with homogeneous Dirichlet boundary condition"
  should be changed to "with a homogeneous Dirichlet boundary
  condiiton". \ydnote{changed}

\item Page 4, Line 14: In equation (2.1), $\Sigma$ has not been
  defined. Please formally define this before giving the equation.
  \ydnote{Moved the equation after $\Sigma$ is defined}

\item Page 4, Line 21: The prior distribution $\mathcal{N}(0,
  \Gamma_{pr})$ assumes the prior mean is 0. This is worthy of some
  comment. Why must the prior mean be 0? \ydnote{It does not have to
    be, we can subtract the mean. An explanation was added}

\item Page 5, Line 15: Add a comma: "Considering the sum of the error
  terms, it is easy..."  \ydnote{changed in text}

\item Page 6, Line 7: Please describe what $\psi$ is in the
  theorem. It is defined mathematically but not described. Only much
  later is it stated that this is the objective
  function. \ydnote{added comment before statment of theorem where
    $\tar$ first appears}

\item Page 6, Line 19-20: "In section 3.2 we relax the constraints on
  $\mathcal{O}$ so that the optimization problem in (3.1) and find
  gradients for the new constraints." This sentence is unclear and
  should be reworded. \ydnote{added short explanation}

\item Page 7, Line 24, 27, 31: The proposition is labeled as
  Proposition 1, but it is refered to as Proposition 2, and relabeled
  Proposition 2 in the appendix. \ydnote{all such errors were fixed}

\item Page 9, Line 6: Please be more exact when refering to "the big
  parentheses" to avoid any chance of confusion. Give the explicit
  formula here as you do for another term earlier in the sentence.
  \ydnote{explicit expression given}

\item Page 18, Line 6: This proposition was previously labeled
  Proposition 1. \ydnote{all such errors were fixed}
\end{itemize}

>>>>

Both referees made great comments that I feel improve the manuscript
substantially, and I would like to thank them for that. I followed up
on every point made. The referees' comments and my replies are listed
below. Below, my replies are colored \ydnote{cyan}. In the revised
manuscript, replies to referee two are in \reftwo{green} and replies
to referee three are in \refthree{red}. Again, thank you for taking
the time and helping me improve this manuscript.

\section{Referee 1}
Preliminary Assessment, Editorial Board Membe.r The manuscript can be
sent to reviewers.

@@

\begin{enumerate}
\item It should be stated in the Abstract whether the work in this
  paper pertains to only linear inverse problems, or if it is
  applicable in general to non-linear inverse problems as well.
  \ydnote{\item Title and abstract now reflect the fact that the paper only
    pertains to linear inverse problems.}

@@

\item In some equations (as seen below in the line comments) operators
are not clearly defined or described before they are given in a
proposition or theorem. Please clearly define all operators both with
mathematical definitions and descriptions (when applicable) before
using them.
\ydnote{\item Corrected, thanks!}

\item Overall, I find the article difficult to follow. I think this can
be improved by properly defining all operators and including section
overviews that give a description of the purpose of each section, and
a brief summary of how this is being accomplished.
\ydnote{\item Added section overviews and operator definitions.}

@@

\begin{itemize}
\item Page 1, Line 39: "In a frequentist settings" should be changed
  to "in a frequentist setting" or "in frequentist
  settings".
  \ydnote{\item Changed in text}

@@

\item Page 3, Line 37: "with homogeneous Dirichlet boundary condition"
  should be changed to "with a homogeneous Dirichlet boundary
  condiiton". \ydnote{\item Changed}

\item Page 4, Line 14: In equation (2.1), $\Sigma$ has not been
  defined. Please formally define this before giving the equation.
  \ydnote{\item Moved the equation after $\Sigma$ is defined}

\item Page 4, Line 21: The prior distribution $\mathcal{N}(0,
  \Gamma_{pr})$ assumes the prior mean is 0. This is worthy of some
  comment. Why must the prior mean be 0?
  \ydnote{\item It does not have to be, we can subtract the mean. An explanation was added}

\item Page 5, Line 15: Add a comma: "Considering the sum of the error
  terms, it is easy..."
  \ydnote{\item Changed in text}

\item Page 6, Line 7: Please describe what $\psi$ is in the
  theorem. It is defined mathematically but not described. Only much
  later is it stated that this is the objective
  function.
  \ydnote{\item Added comment before statment of theorem where
    $\tar$ first appears}

\item Page 6, Line 19-20: "In section 3.2 we relax the constraints on
  $\mathcal{O}$ so that the optimization problem in (3.1) and find
  gradients for the new constraints." This sentence is unclear and
  should be reworded.
  \ydnote{\item Added short explanation}

\item Page 7, Line 24, 27, 31: The proposition is labeled as
  Proposition 1, but it is refered to as Proposition 2, and relabeled
  Proposition 2 in the appendix.
  \ydnote{\item All such errors were fixed}

\item Page 9, Line 6: Please be more exact when refering to "the big
  parentheses" to avoid any chance of confusion. Give the explicit
  formula here as you do for another term earlier in the sentence.
  \ydnote{\item Explicit expression given}

\item Page 18, Line 6: This proposition was previously labeled
  Proposition 1. \ydnote{\item All such errors were fixed}
\end{itemize}
